Bayesian Inference Using Sequential Monte-Carlo Algorithm for Dynamic System Models

### 2020-08-11 conclusion/conclusion.tex
New sevtion

\chapter{Conclusions}

@@

 The inference program was mostly run on multi-core machines, and additional performance

@@

>>>>

\chapter{Conclusion}

@@

 The inference program was mostly run on multi-core machines, and additional scaling-up performance test illustrated the scaling behaviour. When the number of running \verb|Python| process exceeds the number of physical cores, hyperthreading would be enabled but gains not significant improvements with respect to execution time, while increase of average sampling size per second was still observed.

@@

 From this application, some suggestions on ABC SMC implementation could be drawn.
